Draft Exploration

### 2020-04-01 draft_exploration.Rmd
added variable of how many times a player has been drafted to master

hs_signed <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  filter(year >= 1990 & year <= 2009) %>%
  filter(draft_round <= 40) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(hs_signed, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Team",
    y = "Percent of Signed High School Picks to MLB",
    title = "Percent of Signed High School Picks to MLB by Round",
    subtitle = "Data: 1980-2009 Drafts"
  )

@@

>>>>

hs_signed <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))

hs_signed_90_09 <- hs_signed %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  filter(year >= 1990 & year <= 2009) %>%
  filter(draft_round <= 40) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(hs_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Round",
    y = "Percent of Signed High School Picks to MLB",
    title = "Percent of Signed High School Picks to MLB by Round",
    subtitle = "Data: 1980-2009 Drafts"
  )

@@

```{r}
hs_unsigned <- master %>%
  arrange(year) %>%
  group_by(mlbid) %>%
  mutate(draft_numb = row_number()) %>%
  filter(first_name == "Brady" & last_name == "Aiken")
```
